### 2024-06-06 Scripts/Scripts-collection.Rmd
Update Scripts-collection.Rmd

```{r Fig 2g}

my_comparisons <- list(c("Yes", "No"))
df_combined$tetracycline__tetA_log10 <- log10(df_combined$tetracycline__tetA)
ggboxplot(df_combined, x="Diagnosed.Pneumonia", y="tetracycline__tetA_log10",
          color = "Diagnosed.Pneumonia", 
          add = "jitter",add.params = list(size = 2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Diagnosed.Pneumonia), lwd = 0.7) +
  scale_x_discrete(labels = c("No" = "No Pneumonia", "Yes" = "Pneumonia")) +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
  labs(x=NULL,y='Total ARG abundance (log10)',) +  ggtitle('Tetracycline__tetA') +
  # scale_y_continuous(limits=c(-2,2))+
  theme_pubr(base_size = 23,legend ='none',x.text.angle = 30) + 
  ggeasy::easy_center_title() + 
  scale_color_npg()

@@

```{r Fig 2h}

my_comparisons <- list(c("Yes", "No"))

df_combined$multidrug__mexB_log10 <- log10(df_combined$multidrug__mexB)
ggboxplot(df_combined, x="Diagnosed.Pneumonia", y="multidrug__mexB_log10",
          color = "Diagnosed.Pneumonia", 
          add = "jitter",add.params = list(size = 2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Diagnosed.Pneumonia), lwd = 0.7) +
  scale_x_discrete(labels = c("No" = "No Pneumonia", "Yes" = "Pneumonia")) +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
  labs(x=NULL,y='Total ARG abundance (log10)',) +  ggtitle('Multidrug__mexB') +
  theme_pubr(base_size = 23,legend ='none',x.text.angle = 30) + 
  ggeasy::easy_center_title() + 
  scale_color_npg()

```{r Fig 2i}

```{r Fig 2j}

@@

df_species_selected <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\MDS_metrics-bray+species_abundance-species_pneumonia.csv)')
df_species_selected$SamplingSite  <- str_replace_all(df_species_selected$SamplingSite, "-", "")
df_species_selected$variable <- str_split(df_species_selected$variable, "__", simplify = TRUE)[,2]
df_species_selected$variable  <- str_replace_all(df_species_selected$variable, "_", " ")
df_species_selected$variable  <- str_replace_all(df_species_selected$variable, " group", " ")

@@

df_tempral_dyanmics_group_new_criteria <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\OI+WBC+Neutrophils-temporal_dynamics_groups.csv)')
df_tempral_dyanmics_group_new_criteria$Group <- factor(df_tempral_dyanmics_group_new_criteria$Group,levels =c('multiple','stable') )
df_tempral_dyanmics_groups_no_na <- na.omit(df_tempral_dyanmics_groups)
my_comparisons <- list(c('multiple','stable'))
df_tempral_dyanmics_group_new_criteria_OI <- df_tempral_dyanmics_group_new_criteria[!is.na(df_tempral_dyanmics_group_new_criteria$Oxygenation.Index.of.The.Day), ]

@@

>>>>

```{r Fig 2g,h; Fig S3g}

df_combined  <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\argsubtypes_pnuemonia_vs_nonpneumonia.csv)')
df_argtypes  <- df_combined %>%
  select(-c('Diagnosed.Pneumonia', 'Antibiotic.Use'))

# Get the names of the argtypes
argtypes <- colnames(df_argtypes)[!(colnames(df_argtypes) %in% c('SampleID', 'SamplingSite'))]
# Initialize a vector to store the p-values
p_values <- numeric(length(argtypes))
# Perform a Wilcoxon test for each argtype
for (i in seq_along(argtypes)) {
  pneumonia_group <- df_combined[df_combined$Diagnosed.Pneumonia == 'Yes', argtypes[i]]
  non_pneumonia_group <- df_combined[df_combined$Diagnosed.Pneumonia == 'No', argtypes[i]]
  wilcox_test_result <- wilcox.test(pneumonia_group, non_pneumonia_group)
  # Check if the p-value is less than 0.05 and the median of the pneumonia group is greater than the median of the non-pneumonia group
  if (wilcox_test_result$p.value < 0.05 && median(pneumonia_group, na.rm = TRUE) > median(non_pneumonia_group, na.rm = TRUE)) {
    p_values[i] <- wilcox_test_result$p.value
  } else {
    p_values[i] <- NA
  }
}

# Combine the argtypes and p-values into a data frame
df_p_values <- data.frame(Argtype = argtypes, P_Value = p_values)
df_p_values <- na.omit(df_p_values)

### plot based on the p-values for argtypes and argsubtypes
my_comparisons <- list(c("Yes", "No"))

df_combined$tetracycline__tetA_log10 <- log10(df_combined$tetracycline__tetA)
ggboxplot(df_combined, x="Diagnosed.Pneumonia", y="tetracycline__tetA_log10",
          color = "Diagnosed.Pneumonia", #palette =c("#0073C2", "#EFC000","#ffb500"),
        #   add = "dotplot",add.params = list(binwidth = 0.1, dotsize = 0.03))  +
          add = "jitter",add.params = list(size = 2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Diagnosed.Pneumonia), lwd = 0.7) +
  scale_x_discrete(labels = c("No" = "No Pneumonia", "Yes" = "Pneumonia")) +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
  labs(x=NULL,y='Total ARG abundance (log10)',) +  ggtitle('Tetracycline__tetA') +
  theme_pubr(base_size = 23,legend ='none',x.text.angle = 30) + 
  ggeasy::easy_center_title() + 
  scale_color_npg()

### ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
my_comparisons <- list(c("Yes", "No"))

df_combined$multidrug__mexB_log10 <- log10(df_combined$multidrug__mexB)
ggboxplot(df_combined, x="Diagnosed.Pneumonia", y="multidrug__mexB_log10",
          color = "Diagnosed.Pneumonia", #palette =c("#0073C2", "#EFC000","#ffb500"),
          #   add = "dotplot",add.params = list(binwidth = 0.1, dotsize = 0.03))  +
          add = "jitter",add.params = list(size = 2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Diagnosed.Pneumonia), lwd = 0.7) +
  # geom_boxplot(aes(color=Diagnosed.Pneumonia), lwd = 0.7) +
  scale_x_discrete(labels = c("No" = "No Pneumonia", "Yes" = "Pneumonia")) +
  #   stat_boxplot(mapping = aes(color=Diagnosed.Pneumonia),geom = "errorbar",width=0.05)  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
  #   yscale("log10",.format = T)  +
  labs(x=NULL,y='Total ARG abundance (log10)',) +  ggtitle('Multidrug__mexB') +
  # scale_y_continuous(limits=c(-2,2))+
  theme_pubr(base_size = 23,legend ='none',x.text.angle = 30) + 
  ggeasy::easy_center_title() + 
  scale_color_npg()

### ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
my_comparisons <- list(c("Yes", "No"))

df_combined$tetracycline__tetB_log10 <- log10(df_combined$tetracycline__tetB)
ggboxplot(df_combined, x="Diagnosed.Pneumonia", y="tetracycline__tetB_log10",
          color = "Diagnosed.Pneumonia", #palette =c("#0073C2", "#EFC000","#ffb500"),
          #   add = "dotplot",add.params = list(binwidth = 0.1, dotsize = 0.03))  +
          add = "jitter",add.params = list(size = 2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Diagnosed.Pneumonia), lwd = 0.7) +
  # geom_boxplot(aes(color=Diagnosed.Pneumonia), lwd = 0.7) +
  scale_x_discrete(labels = c("No" = "No Pneumonia", "Yes" = "Pneumonia")) +
  #   stat_boxplot(mapping = aes(color=Diagnosed.Pneumonia),geom = "errorbar",width=0.05)  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
  #   yscale("log10",.format = T)  +
  labs(x=NULL,y='Total ARG abundance (log10)',) +  ggtitle('Tetracycline__tetB') +
  # scale_y_continuous(limits=c(-2,2))+
  theme_pubr(base_size = 23,legend ='none',x.text.angle = 30) + 
  ggeasy::easy_center_title() + 
  scale_color_npg()

### ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
my_comparisons <- list(c("Yes", "No"))

df_combined$aminoglycoside__aph.3...IIb_log10 <- log10(df_combined$aminoglycoside__aph.3...IIb)
ggboxplot(df_combined, x="Diagnosed.Pneumonia", y="aminoglycoside__aph.3...IIb_log10",
          color = "Diagnosed.Pneumonia", #palette =c("#0073C2", "#EFC000","#ffb500"),
          #   add = "dotplot",add.params = list(binwidth = 0.1, dotsize = 0.03))  +
          add = "jitter",add.params = list(size = 2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Diagnosed.Pneumonia), lwd = 0.7) +
  # geom_boxplot(aes(color=Diagnosed.Pneumonia), lwd = 0.7) +
  scale_x_discrete(labels = c("No" = "No Pneumonia", "Yes" = "Pneumonia")) +
  #   stat_boxplot(mapping = aes(color=Diagnosed.Pneumonia),geom = "errorbar",width=0.05)  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
  #   yscale("log10",.format = T)  +
  labs(x=NULL,y='Total ARG abundance (log10)',) +  ggtitle('Aminoglycoside__aph.3...IIb') +
  # scale_y_continuous(limits=c(-2,2))+
  theme_pubr(base_size = 23,legend ='none',x.text.angle = 30) + 
  ggeasy::easy_center_title() + 
  scale_color_npg()

@@

```{r Fig 2i,j; Fig S3h}

df_target_argsubtype_icu_day  <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\argsubtype-pneumonia-icu_day.csv)')
df_target_argsubtype_icu_day$multidrug__mexE_log10 <- log10(df_target_argsubtype_icu_day$multidrug__mexE)
df_target_argsubtype_icu_day$multidrug__smeB_log10 <- log10(df_target_argsubtype_icu_day$multidrug__smeB)
df_target_argsubtype_icu_day$aminoglycoside__aph.3...IIb_log10 <- log10(df_target_argsubtype_icu_day$aminoglycoside__aph.3...IIb)
df_target_argsubtype_icu_day$multidrug__smeC_log10 <- log10(df_target_argsubtype_icu_day$multidrug__smeC)

### Box plot for each argsubtype
my_comparisons <- list(c("[0,7]", ">28"), c("(7,14]", ">28"), c( "(14,21]",">28"), c("(21,28]", ">28"))
# my_comparisons <- list(c("(7,14]","[0,7]"), c("(14,21]","[0,7]"), c( "(21,28]","[0,7]"), c(">28","[0,7]"))
df_target_argsubtype_icu_day$Sample.Day_ICU_fac2 <- factor(df_target_argsubtype_icu_day$Sample.Day_ICU_fac2, levels = c("[0,7]", "(7,14]", "(14,21]", "(21,28]", ">28"))

ggboxplot(df_target_argsubtype_icu_day, x="Sample.Day_ICU_fac2", y="multidrug__mexE_log10",
          color = "Sample.Day_ICU_fac2", #palette =c("#0073C2", "#EFC000","#ffb500"),
        #   add = "dotplot",add.params = list(binwidth = 0.1, dotsize = 0.03))  +
          add = "jitter",add.params = list(size = 2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Sample.Day_ICU_fac2), lwd = 0.7) +
  # geom_boxplot(aes(color=Sample.Day_ICU_fac2), lwd = 0.7) +
  # scale_x_discrete(labels = c("No" = "No Pneumonia", "Yes" = "Pneumonia")) +
#   stat_boxplot(mapping = aes(color=Diagnosed.Pneumonia),geom = "errorbar",width=0.05)  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
#   yscale("log10",.format = T)  +
  labs(x='Days in the ICU',y='Total ARG abundance (log10)',) +  ggtitle('Multidrug__mexE') +
  # scale_y_continuous(limits=c(-2,2))+
  theme_pubr(base_size = 23,legend ='none',x.text.angle = 50) + 
  ggeasy::easy_center_title() + 
  scale_color_npg()

#---------------------------------------------------------------------------------------

ggboxplot(df_target_argsubtype_icu_day, x="Sample.Day_ICU_fac2", y="multidrug__smeB_log10",
          color = "Sample.Day_ICU_fac2", #palette =c("#0073C2", "#EFC000","#ffb500"),
        #   add = "dotplot",add.params = list(binwidth = 0.1, dotsize = 0.03))  +
          add = "jitter",add.params = list(size = 2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Sample.Day_ICU_fac2), lwd = 0.7) +
  # geom_boxplot(aes(color=Sample.Day_ICU_fac2), lwd = 0.7) +
  # scale_x_discrete(labels = c("No" = "No Pneumonia", "Yes" = "Pneumonia")) +
#   stat_boxplot(mapping = aes(color=Diagnosed.Pneumonia),geom = "errorbar",width=0.05)  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
#   yscale("log10",.format = T)  +
  labs(x='Days in the ICU',y='Total ARG abundance (log10)',) +  ggtitle('Multidrug__smeB') +
  # scale_y_continuous(limits=c(-2,2))+
  theme_pubr(base_size = 23,legend ='none',x.text.angle = 50) + 
  ggeasy::easy_center_title() + 
  scale_color_npg()

#---------------------------------------------------------------------------------------

ggboxplot(df_target_argsubtype_icu_day, x="Sample.Day_ICU_fac2", y="aminoglycoside__aph.3...IIb_log10",
          color = "Sample.Day_ICU_fac2", #palette =c("#0073C2", "#EFC000","#ffb500"),
        #   add = "dotplot",add.params = list(binwidth = 0.1, dotsize = 0.03))  +
          add = "jitter",add.params = list(size = 2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Sample.Day_ICU_fac2), lwd = 0.7) +
  # geom_boxplot(aes(color=Sample.Day_ICU_fac2), lwd = 0.7) +
  # scale_x_discrete(labels = c("No" = "No Pneumonia", "Yes" = "Pneumonia")) +
#   stat_boxplot(mapping = aes(color=Diagnosed.Pneumonia),geom = "errorbar",width=0.05)  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
#   yscale("log10",.format = T)  +
  labs(x='Days in the ICU',y='Total ARG abundance (log10)',) +  ggtitle('Aminoglycoside__aph.3...IIb') +
  # scale_y_continuous(limits=c(-2,2))+
  theme_pubr(base_size = 23,legend ='none',x.text.angle = 50) + 
  ggeasy::easy_center_title() + 
  scale_color_npg()

#---------------------------------------------------------------------------------------

ggboxplot(df_target_argsubtype_icu_day, x="Sample.Day_ICU_fac2", y="multidrug__smeC_log10",
          color = "Sample.Day_ICU_fac2", #palette =c("#0073C2", "#EFC000","#ffb500"),
        #   add = "dotplot",add.params = list(binwidth = 0.1, dotsize = 0.03))  +
          add = "jitter",add.params = list(size = 2.4, alpha = 0.8))  +
  geom_boxplot(aes(color=Sample.Day_ICU_fac2), lwd = 0.7) +
  # geom_boxplot(aes(color=Sample.Day_ICU_fac2), lwd = 0.7) +
  # scale_x_discrete(labels = c("No" = "No Pneumonia", "Yes" = "Pneumonia")) +
#   stat_boxplot(mapping = aes(color=Diagnosed.Pneumonia),geom = "errorbar",width=0.05)  +
  stat_compare_means(comparisons = my_comparisons,label = "p.label",size=7,
                     vjust=.15,tip.length= c(0,0,0)) + 
#   yscale("log10",.format = T)  +
  labs(x='Days in the ICU',y='Total ARG abundance (log10)',) +  ggtitle('Multidrug__smeC') +
  # scale_y_continuous(limits=c(-2,2))+
  theme_pubr(base_size = 23,legend ='none',x.text.angle = 50) + 
  ggeasy::easy_center_title() + 
  scale_color_npg()

```
### Figure S2
### --------------------------------------------------------------------------------------------------------------------------------------------

@@

df_species_selected <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\MDS_metrics-bray+species_abundance-species_pneumonia.csv)') # save in the same file 'MDS_metrics-bray-species_profiles_pneumonia.txt'
df_species_selected$SamplingSite  <- str_replace_all(df_species_selected$SamplingSite, "-", "")
df_species_selected$variable <- str_split(df_species_selected$variable, "__", simplify = TRUE)[,2]
df_species_selected$variable  <- str_replace_all(df_species_selected$variable, "_", " ")
df_species_selected$variable  <- str_replace_all(df_species_selected$variable, " group", " ")

@@

df_tempral_dyanmics_group_new_criteria <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\OI+Neutrophils-temporal_dynamics_groups.csv)')
df_tempral_dyanmics_group_new_criteria$Group <- factor(df_tempral_dyanmics_group_new_criteria$Group,levels =c('multiple','stable') )
df_tempral_dyanmics_groups_no_na <- na.omit(df_tempral_dyanmics_groups)
my_comparisons <- list(c('multiple','stable'))
df_tempral_dyanmics_group_new_criteria_OI <- df_tempral_dyanmics_group_new_criteria[!is.na(df_tempral_dyanmics_group_new_criteria$Oxygenation.Index.of.The.Day), ]

@@

### Figure 3
### --------------------------------------------------------------------------------------------------------------------------------------------
